### 2016-08-26 ms/ms.tex
finished first full draft of manuscript, added plants to turnover analyses

\begin{figure}
  \centering
  \includegraphics[width=.8\textwidth]{../analysis/changePoint/plotting/communitiesSkanky.pdf}
  \caption{The community (i.e., module or compartment) membership
    between network changing points. Two representative assembling
    hedgerows are depicted. In the top panel, species are grouped by
    community. The bottom panels visualize the flow of species between
    communities between changing points. }
  \label{fig:changePoints2}
\end{figure}
\clearpage

@@

\begin{figure}
  \centering
  \includegraphics[width=.7\textwidth]{../analysis/variability/figures/turnover_panels.pdf}
  \caption{The species, interaction and weighted interactions turnover
    of plant-pollinator networks at non-assembling field margins
    sites, assembling hedgerows, and non-assembling, mature
    hedgerows. Rates of species and interaction turnover were similar
    between site types, though mature hedgerows has marginally
    significantly less pollinator turnover.  However, when
    interactions where weighted by their similarity, both hedgerow
    types had higher turnover that unrestored field margins. Boxplots
    represent medians (black horizontal line) first and third
    quartiles (box perimeter) and extremes (whiskers). }
  \label{fig:beta}
\end{figure}
\clearpage

>>>>

\begin{figure}
  \centering
  \includegraphics[width=.9\textwidth]{../analysis/changePoint/plotting/communitiesSkanky.pdf}
  \caption{The community (i.e., module or compartment) membership
    between network changing points. Two representative assembling
    hedgerows are depicted. In the top panel, species are grouped by
    community. The bottom panels visualize the flow of species between
    communities between changing points. }
  \label{fig:changePoints2}
\end{figure}
\clearpage

@@

\begin{figure}
  \centering
  \includegraphics[width=.8\textwidth]{../analysis/variability/figures/turnover_panels.pdf}
  \caption{The species, interaction and weighted interactions turnover
    of plant-pollinator networks at non-assembling field margins
    sites, assembling hedgerows, and non-assembling, mature
    hedgerows. Rates of species and interaction turnover were similar
    between site types, though mature hedgerows has marginally
    significantly less pollinator turnover.  However, when
    interactions where weighted by their similarity, both hedgerow
    types had higher turnover that unrestored field margins. Boxplots
    represent medians (black horizontal line) first and third
    quartiles (box perimeter) and extremes (whiskers). }
  \label{fig:beta}
\end{figure}
\clearpage
